Word learning at the semantics pragmatics interface

### 2020-03-18 paper/supplementary_material.Rmd
add model comparison to check for item effects in exp 1 and 3

The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age. As a first step, we replicate earlier work showing that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge. In a second experiment, we show that children make inferences about word meanings based on common ground. In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.

@@

In the final section, we turn to the process by which information is integrated. We contrast the process of rational Bayesian inference we introduced in our model with a process in which one type of inference is given more weight. As part of this, we also explore alternative ways to think about developmental change in the integration process.

@@

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal of Experiment 1 was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object. That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familiar object that was presented with the novel object.

@@

We tested a total number of `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1). All children were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocol no. 19960)

@@

The experiment was presented as an interactive picture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests. Each experiment started with two training trials in which the speaker requested a known object (car and ball).

In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also changed from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

@@

```{r, echo=T}
# prior_me <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")

bm_me <- readRDS("../saves/bm_me.rds")
```

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects.  The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.

The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept. The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the mutual exclusivity inference depended on age as well as the familiar object.

@@

```{r table2, echo=T}
chance_prior <- prior_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf,2), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

@@

Table \@ref(tab:table2) compares children's correct responses to a level expected by chance (50%). We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.

@@

# prior_comb <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
#                     data = comb_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_comb,
#           cores = 4,
#           chains = 4,
#           inits = 0,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_comb.rds")

bm_comb <- readRDS("../saves/bm_comb.rds")
```

@@

The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions. The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`). Figure \@ref(fig:fig3)B visualizes the model. Taken together, the results show that children responded to the way the two inferences were aligned with one another.

@@

## Modelling framework

@@

On the other hand, we compared models based on Bayes factors which were calculated from the marginal likelihoods of each model given the data. For this analysis, we treated age continuously. We first calculated the marginal log-likelihood for each model and then computed Bayes factors by subtracting the log-likelihoods for the models involved in the comparison and then exponentiating the result (see file `model_comparison.Rmd` in the associated online repository). Table \@ref(tab:table3) lists the Bayes factors for the different model comparisons. The results show that the *integration model*, by far, outperformed all the other models. When comparing the lesion models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.

@@

```{r table3}
model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration vs no word knowledge" = "prag_vs_global",
                            "integration vs no common ground" = "prag_vs_flat",
                            "integration vs no mutual exclusivity" = "prag_vs_prior",
                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
                            "no word knowledge vs no common ground" = "global_vs_prior",
                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
        `Bayes factor` = format(round(exp(logBF),2), trim = T, justify = "right", digits = 2))%>%
  select(-logBF, -model)

@@

\begin{equation} 
P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
\end{equation}

@@

We compared models based on correlations and Bayes factors. Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and object. Even though model predictions and data are closely aligned for all models, the *integration model* shows the highest correlation in all age groups. Next we directly compared models based using Bayes factors (see Table \@ref(tab:table4)). We also included the prediction *integration model* into this analysis.

@@

```{r table4}
model_comp_pred <- readRDS("../saves/expl_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration (explanation) vs integration (prediction)" = "fb_vs_free",
                            "integration (explanation) vs mixture" = "fb_vs_mixture",
                            "integration (prediction) vs mixture" = "free_vs_mixture",
                            "integration (explanation) vs developmental mixture" = "fb_vs_dev_mixture",
                            "integration (prediction) vs developmental mixture" = "free_vs_dev_mixture",
                            "developmental mixture vs mixture" = "dev_mixture_vs_mixture"),
        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
  select(-logBF, -model)

>>>>

The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age. As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning. In experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge. In a second experiment, we show that children make inferences about word meanings based on common ground. In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.

@@

In the final section, we turn to the process by which information is integrated. We contrast the process of rational Bayesian inference we introduced in our model with a biased integration process in which one type of inference is given more weight. As part of this, we also explore alternative ways to think about developmental change in the integration process.

@@

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object. That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familiar object that were presented alongside the novel object.

@@

We tested a total number of `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1). All children were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocol no. 19960).

@@

The experiment was presented as an interactive picture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal standing on a little hill between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests. Each experiment started with two training trials in which the speaker requested known objects (car and ball).

In experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also changed from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

@@

```{r, echo=T}
# prior_me <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")
# 
# 
# bm_me2 <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")

bm_me <- readRDS("../saves/bm_me.rds")

bm_me2 <- readRDS("../saves/bm_me2.rds")

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects.  The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.

The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect. Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights. The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred. WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data. The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)). Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept. The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the strength  of the mutual exclusivity inference depended on age as well as the familiar object.

```{r table2, echo=T}

me_waic <- brms::waic(bm_me, bm_me2, compare = F)

me_weights <- model_weights(bm_me, bm_me2, weights = "waic")

me_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(me_waic$loos$bm_me$estimates["waic","Estimate"],me_waic$loos$bm_me2$estimates["waic","Estimate"]),2),
  SE = round(c(me_waic$loos$bm_me$estimates["waic","SE"],me_waic$loos$bm_me2$estimates["waic","SE"]),2),
  weight = round(c(me_weights[1],me_weights[2]))
)

knitr::kable(me_comp, caption = "Model comparison in experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
```

@@

```{r table3, echo=T}
chance_prior <- prior_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf,2), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

@@

Table \@ref(tab:table3) compares children's correct responses to a level expected by chance (50%). We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.

@@

# prior_comb <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
#                     data = comb_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_comb,
#           cores = 4,
#           chains = 4,
#           inits = 0,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_comb.rds")
# 
# bm_comb2 <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | agent),
#                     data = comb_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_comb,
#           cores = 4,
#           chains = 4,
#           inits = 0,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_comb2.rds")

bm_comb <- readRDS("../saves/bm_comb.rds")

bm_comb2 <- readRDS("../saves/bm_comb2.rds")

@@

The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions. The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`). A model lacking `object` as a random effect provided a much poorer fit, suggesting substantial variation across objects (see Table \@ref(tab:table4)). Figure \@ref(fig:fig3)B visualizes the model. Taken together, the results show that children responded to the way the two inferences were aligned with one another.

```{r table4, echo=T}

comb_waic <- brms::waic(bm_comb, bm_comb2, compare = F)

comb_weights <- model_weights(bm_comb, bm_comb2, weights = "waic")

comb_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(comb_waic$loos$bm_comb$estimates["waic","Estimate"],comb_waic$loos$bm_comb2$estimates["waic","Estimate"]),2),
  SE = round(c(comb_waic$loos$bm_comb$estimates["waic","SE"],comb_waic$loos$bm_comb2$estimates["waic","SE"]),2),
  weight = round(c(comb_weights[1],comb_weights[2]))
)

knitr::kable(comb_comp, caption = "Model comparison in experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
```

@@

## Modeling framework

@@

On the other hand, we compared models based on Bayes factors which were calculated from the marginal likelihoods of each model given the data. For this analysis, we treated age continuously. We first calculated the marginal log-likelihood for each model and then computed Bayes factors by subtracting the log-likelihoods for the models involved in the comparison and then exponentiating the result (see file `model_comparison.Rmd` in the associated online repository). Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons. The results show that the *integration model*, by far, outperformed all the other models. When comparing the lesion models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.

@@

```{r table5}
model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration vs no word knowledge" = "prag_vs_global",
                            "integration vs no common ground" = "prag_vs_flat",
                            "integration vs no mutual exclusivity" = "prag_vs_prior",
                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
                            "no word knowledge vs no common ground" = "global_vs_prior",
                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
        `Bayes factor` = format(round(exp(logBF),2), trim = T, justify = "right", digits = 2))%>%
  select(-logBF, -model)

@@

\begin{equation} 
to be adjusted .... P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
\end{equation}

@@

We compared models based on correlations and Bayes factors. Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and object. Even though model predictions and data are closely aligned for all models, the *integration model* shows the highest correlation in all age groups. Next we directly compared models based using Bayes factors (see Table \@ref(tab:table6)). We also included the prediction *integration model* into this analysis.

@@

```{r table6}
model_comp_pred <- readRDS("../saves/expl_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration (explanation) vs integration (prediction)" = "fb_vs_free",
                            "integration (explanation) vs mixture" = "fb_vs_mixture",
                            "integration (prediction) vs mixture" = "free_vs_mixture",
                            "integration (explanation) vs developmental mixture" = "fb_vs_dev_mixture",
                            "integration (prediction) vs developmental mixture" = "free_vs_dev_mixture",
                            "developmental mixture vs mixture" = "dev_mixture_vs_mixture"),
        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
  select(-logBF, -model)
